manuscript_notes

### 2024-11-26 notes/manuscript_notes.Rmd
add note

- add refs for some websites I consulted
- check the references in the ms to various parts of the supplementary material
- check legends of all Figures, and add more info if needed

>>>>

- add figures of the prior predictive checks in Tutorial_2a.html

- add refs for some websites I consulted

- check the references in the ms to various parts of the supplementary material

- check legends of all Figures, and add more info if needed
